The MACE is essentially unidimensional: Bifactor models of the `Maltreatment and Abuse Chronology of Exposure' scale

### 2022-08-08 manuscript/main.tex
manuscipt edits (2022-08-07c)

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}             % fancy latex tables
\usepackage[export]{adjustbox}    % center wide tables on page
\usepackage{setspace}             % adjust caption linespacing

@@

@@

@@

In addition to the MACE, participants in both samples completed a number of additional self-report measures. Participants in the original sample completed multiple measures concerning psychiatric symptoms; these have already been reported \citep{teicher2015maltreatment}. The participants in the replication sample completed three additional self-report measures all assessing negative symptoms and motivation for rewards. Specifically, participants completed the Motivation and Pleasure scale \citep{llerena2013motivation}, the Self-evaluation of Negative Symptoms scale \citep{dollfus2016self}, and the revised Behavioral Inhibition / Behavioral Activation scale \citep{pagliaccio2016revising}.

Following best practices for online research \citep{zorowitz2021inattentive}, several attention checks were embedded in the secondary self-report measures filled out by the replication sample. Specifically, we used infrequency items which are questions for which all  or virtually all attentive participants should provide the same response. Specifically, we used the following questions:

@@

>>>>

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}             % fancy latex tables
\usepackage[export]{adjustbox}    % center wide tables on page
\usepackage{setspace}             % adjust caption linespacing 
\usepackage{multibib}             % references in supplement

@@

% setup supplementary references
\newcites{SM}{Supplementary references}

@@

\textbf{Background}

\textbf{Methods}

\textbf{Results}

\textbf{Conclusions}

@@

In addition to the MACE, participants in both samples completed a number of additional self-report measures. Participants in the original sample completed multiple measures concerning psychiatric symptoms; these have already been reported \citepSM{teicher2015maltreatment}. The participants in the replication sample completed three additional self-report measures all assessing negative symptoms and motivation for rewards. Specifically, participants completed the Motivation and Pleasure scale \citepSM{llerena2013motivation}, the Self-evaluation of Negative Symptoms scale \citepSM{dollfus2016self}, and the revised Behavioral Inhibition / Behavioral Activation scale \citepSM{pagliaccio2016revising}.

Following best practices for online research \citepSM{zorowitz2021inattentive}, several attention checks were embedded in the secondary self-report measures filled out by the replication sample. Specifically, we used infrequency items which are questions for which all  or virtually all attentive participants should provide the same response. Specifically, we used the following questions:

@@

\bibliographystyleSM{apalike}
\bibliographySM{main}
